---
output:
  github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Introduction

Welcome to my Shiny Server!  This repo contains everything needed to deploy a Shiny Server on Google Cloud.

Check out my app [portfolio](https://blog.sqwerl.life/shiny/) to see them in action!

## Build Triggers

There is a [build trigger](https://console.cloud.google.com/cloud-build/triggers) setup for this repo.  Every time a change is pushed, the image is rebuilt using the included Dockerfile.  It's pretty great!

## Deploying on Google Cloud

Here's the code I use to deploy a new VM with the updated image:

```{r, eval = FALSE}
library(googleComputeEngineR)

vm <- gce_vm(
  "avp-shiny-master", 
  predefined_type = "g1-small", 
  template = "shiny",
  dynamic_image = gce_tag_container("shiny", project = "avp-consulting")
  )
```

Once the new VM is available, then we can switch it to the static IP and turn off the old machine.

## Deployment Summary

  1. Make changes and push to Github (and trigger Cloud Build)
  2. Confirm the Cloud Build is successful
  3. Spin up a new VM with the updated build image
  4. Confirm the new VM is up and running
  5. Point the new VM to my static IP address -- [link](https://console.cloud.google.com/networking/addresses/list)
  6. Delete the old VM
